The Strucplot Framework:\\ Visualizing Multi-way Contingency Tables with \pkg{vcd}

### 2006-10-10 trunk/vcd/paper/Strucplot/JSS.Rnw
Cosmetics.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/vcd@587 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\noindent (Note that \code{HEC}, a \class{structable} object, already includes a
splitting information which simply gets overloaded in this example.) 
For compatibility with \codefun{mosaicplot} in base \proglang{R},
the \codefun{mosaic} function also allows the use of a \code{"direction"} 
argument taking a vector of \code{"h"} and
\code{"v"} characters:

@@

\noindent since we first push the $k_1$ viewports for the levels of the
first dimension, then, for \emph{each} of those, the $k_2$ levels of
the second dimension, etc. If the number of levels is equal ($k$) for
all dimensions, this simplifies to:

>>>>

\noindent (Note that \code{HEC}, a \class{structable} object, already
includes a splitting information which simply gets overloaded in this
example.)  For compatibility with \codefun{mosaicplot} in base
\proglang{R}, the \codefun{mosaic} function also allows the use of a
\code{direction} argument taking a vector of \code{"h"} and \code{"v"}
characters:

@@

\noindent since we first push the $k_1$ viewports for the levels of the
first dimension, then, for \emph{each} of these, the $k_2$ levels of
the second dimension, etc. If the number of levels is equal ($k$) for
all dimensions, $T_d$ simplifies to
